\documentclass[letter,10pt]{moderncv}
\usepackage[scale=0.8]{geometry}
\usepackage[backend=biber,sorting=ydnt,style=authoryear,maxnames=100]{biblatex}

\moderncvstyle{casual}
\moderncvcolor{black}

\name{Trevor}{Elliott}
\email{awesomelyawesome@gmail.com}
\phone[mobile]{(503) 936-6575}
\social[github]{elliottt}

\renewbibmacro*{date}{}
\renewbibmacro*{date+extrayear}{}
\renewbibmacro*{issue+date}{}
\newcommand*{\bibyear}{}

\defbibenvironment{bibliography}
  {\list
    {\iffieldequals{year}{\bibyear}
       {}
       {\printfield{year}%
        \savefield{year}{\bibyear}}}
    {\setlength{\topsep}{0pt}%
     \setlength{\labelwidth}{\hintscolumnwidth}%
     \setlength{\labelsep}{\separatorcolumnwidth}%
     \leftmargin\labelwidth%
     \advance\leftmargin\labelsep}%
     \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
{\item}

\nocite{*}
\addbibresource{publications.bib}

\begin{document}

\makecvtitle

\section{Experience}

\cventry{2022-Present}{Principal Engineer}{Fastly}{Portland, OR}
  {}{Working on the Compute@Edge team}

\cventry{2019--2022}{Infrastructure Engineer}{Stripe}{Portland, OR}
  {}{Working on the \href{https://sorbet.org}{sorbet} typechecker and compiler for ruby.
  \begin{itemize}%
  \item Key contributor on the sorbet compiler, implementing optimizations and
    improving coverage for the ruby language. Generated native code with llvm,
    targeting the ruby vm's c api.
  \item Implemented type-system features and improved type-checker runtime performance.
  \item Mentored an intern on the sorbet compiler project, and organized/ran
    regular meetings with external contributors from other companies.
  \end{itemize}}

\cventry{2017--2019}{Compiler Engineer}{Groq, Inc.}{Portland, OR}
  {}{Worked on a compiler for tensorflow models, targeting a custom ASIC
  that accelerates inference. Focused on compiler performance and optimization
  of results.}

\cventry{2007--2017}{Engineer and Researcher}{Galois, Inc.}{Portland, OR}
  {}{Contributed to a broad range of projects, notably:
  \begin{itemize}%
  \item Developed domain specific languages in Haskell, including the
    \href{https://github.com/galoisinc/msf-haskell}{msf-haskell} metasploit DSL
    and the \href{https://github.com/galoisinc/ivory}{Ivory} DSL for memory-safe
    embedded programming
  \item Developed and contributed to multiple full language implementations,
    including \href{https://github.com/galoisinc/cryptol}{Cryptol} and the
    \href{https://github.com/galoisinc/salty}{Salty} GR(1) reactive synthesis DSL
  \item Implemented the HaNS network stack
  \item Aided ASIC design and verification for lightweight cryptographic
    primitives from Cryptol specifications
  \end{itemize}}

\cventry{2004--2007}{Developer}{CollegeNET}{Portland, OR}
  {}{Helped to transition a large desktop application to a suite of web
  services, and developed tools based off of those web services. Also assisted
  with some front-end web development, and implemented an LDAP-based
  authentication system.}

\cventry{2002--2004}{Technical Support}{CollegeNET}{Portland, OR}
  {}{Provided technical support to a large client base.}

\section{Education}

\cventry{2008}{B.S. Computer Science}{Portland State University}{Portland, OR}{}{}

\section{Open Source Projects}
\cvitem{\href{https://github.com/sorbet/sorbet}{sorbet}}
  {The sorbet typechecker and compiler for ruby}
\cvitem{\href{https://github.com/galoisinc/cereal}{cereal}}
  {Haskell library for fast binary format parsing/rendering}
\cvitem{\href{https://github.com/galoisinc/ivory}{ivory}}
  {Haskell EDSL for memory-safe embedded programming}
\cvitem{\href{https://github.com/galoisinc/salty}{salty}}
  {Reactive synthesis DSL for GR(1) specifications}
\cvitem{\href{https://github.com/galoisinc/hans}{HaNS}}
  {A TCP/IP network stack implemented in haskell}
\cvitem{\href{https://github.com/galoisinc/cryptol}{Cryptol}}
  {DSL for implementation and verification of cryptographic algorithms}
\cvitem{\href{https://github.com/galoisinc/halvm}{HaLVM}}
  {Port of the GHC runtime to the Xen hypervisor}
\cvitem{\href{https://github.com/elliottt/llvm-pretty}{llvm-pretty}}
  {An EDSL for generating textual llvm bitcode}
\cvitem{\href{https://github.com/elliottt/huff}{huff}}
  {A fast-forward based classical planning EDSL}

\section{Skills}
\cvitem{Languages}{haskell, c/c++, rust, java, javascript, fsharp, ocaml,
  python, ruby, lua, assembly (x86, arm), coq, isabelle/hol, shell scripting}
\cvitem{Tools}{z3, smt-lib, lldb, gdb, bazel, gnu make, vim/neovim}

\printbibliography[title=Publications]

\end{document}
